Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-25 paper.tex
Compact sums

\begin{figure}[p]
\setlength{\mathindent}{1em}
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
\setlength{\abovecaptionskip}{0pt}
\begin{framed}
\begin{align}
    \intertext{A copy of these variables and constraints is created for each skipper $\sigma$:\smallskip}
    &\forall \tau \in \{0 \nldots t{-}1\}: \timeSlot[{\tau}] \in \{{-}2 \nldots t{-}1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V1} \\
    &\forall i \in \{0 \nldots f{-}1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
    &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
    &\begin{alignedat}{3}
    &\hspace*{1em} \state[{i}] = \FIRST &\ &\Leftrightarrow&&\ \timeSlot[{i \cdot m}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{i\cdot m{+}1 \nldots i \cdot m{+}m{-}2\} : \timeSlot[{j}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[{(i{+}1)m {-} 1}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i{+}1){-}1\} : \timeSlot[j] = {-}1 \\
    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i{+}1){-}1\} : \timeSlot[j] = {-}2
    \end{alignedat} \nonumber \\
    &\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n{-}1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
    &\validStateSequence(\state) \label{C3} \tag{C3} \\[0.1cm]
    & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] \in \{0,1\} \label{V3} \tag{V3} \\
    & \totalChanges \in \mathbb{N} \label{V4} \tag{V4} \\
    & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] = 1 \Leftrightarrow \state[{i}] = \BYE \wedge \state[{i{+}1}] \neq \BYE \label {C4} \tag{C4} \\
    & \totalChanges = \textstyle\sum_{i=0}^{f{-}2} \change[{i}] \label{C5} \tag{C5}
\end{align}
\end{framed}\begin{framed}
\begin{align}
    \intertext{Match and temporal perspectives:\smallskip}
    & \forall i \in \{0 \nldots n{-}2\} : \forall j \in \{ i{+}1 \nldots n{-}1 \} : \nonumber \\
    & \hspace*{1em} \match[{i,j}] \in \{0..t{-}1\} \tag{V5} \label{V5} \\
    & \hspace*{1em} \match[{j,i}] \equiv \match[{i,j}] \nonumber \\
    & \hspace*{1em} \forall k \in \{0 \nldots t{-}1 \} : \nonumber \\
    & \hspace*{2em} \match[{i,j}] = k \Leftrightarrow \sigma[{i}].\timeSlot[{k}] = j \wedge \sigma[{j}].\timeSlot[{k}] = i \tag{C6} \label{C6} \\[0.1cm]
    & \forall i \in \{0 \nldots n{-}2\} : \forall j \in \{ i{+}1 \nldots n{-}1 \} \nonumber : \\
    & \hspace*{1em} \modMatch[{i,j}] \in \{0..f{-}1\} \label{V6} \tag{V6} \\
    & \hspace*{1em} \modMatch[{j,i}] \equiv \modMatch[{i,j}] \nonumber  \\
    & \hspace*{1em} \modMatch[{i,j}] = \match[{i,j}] / m \tag{C7} \label{C7} \\
    & \forall i \in \{0 \nldots n{-}1 \} : \allDifferent(\modMatch[{i}]) \tag{C8} \label{C8} \\[0.1cm]
    & \forall \tau \in \{0 \nldots t{-}1 \} : \nonumber \\
    & \hspace*{1em} \timeVar[{\tau}] \in \{(0,1) \nldots (n{-}2,n{-}1)\} \tag{V7} \label{V7} \\
    & \hspace*{1em} \forall i \in \{0 \nldots n{-}2\} : \forall  j \in \{ i{+}1 \nldots n{-}1 \} : \timeVar[{\tau}] = (i,j) \Leftrightarrow \match[{i,j}] = \tau \tag{C9} \label{C9} \\[0.1cm]
    & \totalBoatChanges = \textstyle\sum_{i=0}^{n{-}1} \sigma[{i}].\totalChanges  \label{V8} \tag{V8} \\
    & \minimise(\totalBoatChanges) \label{C10} \tag{C10}
\end{align}
\end{framed}
\caption{Our constraint model, from a skipper perspective (top) and a match and
temporal perspective (below). The number of skippers is $n$, and $m$ is the
number of matches in a flight. The number of flights is $f = \lceil n(n-1)/m
\rceil$, and there are $t = n(n-1)/2$ matches in total.}\label{model:stage1}
\end{figure}

>>>>

\begin{figure}[p]
\setlength{\mathindent}{1em}
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
\setlength{\abovecaptionskip}{0pt}
\begin{framed}
\begin{align}
    \intertext{A copy of these variables and constraints is created for each skipper $\sigma$:\smallskip}
    &\forall \tau \in \{0 \nldots t{-}1\}: \timeSlot[{\tau}] \in \{{-}2 \nldots t{-}1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V1} \\
    &\forall i \in \{0 \nldots f{-}1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
    &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
    &\begin{alignedat}{3}
    &\hspace*{1em} \state[{i}] = \FIRST &\ &\Leftrightarrow&&\ \timeSlot[{i \cdot m}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{i\cdot m{+}1 \nldots i \cdot m{+}m{-}2\} : \timeSlot[{j}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[{(i{+}1)m {-} 1}] \geq 0 \\
    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i{+}1){-}1\} : \timeSlot[j] = {-}1 \\
    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i{+}1){-}1\} : \timeSlot[j] = {-}2
    \end{alignedat} \nonumber \\
    &\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n{-}1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
    &\validStateSequence(\state) \label{C3} \tag{C3} \\[0.1cm]
    & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] \in \{0,1\} \label{V3} \tag{V3} \\
    & \totalChanges \in \mathbb{N} \label{V4} \tag{V4} \\
    & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] = 1 \Leftrightarrow \state[{i}] = \BYE \wedge \state[{i{+}1}] \neq \BYE \label {C4} \tag{C4} \\
    & \totalChanges = \textstyle\sum \change \label{C5} \tag{C5}
\end{align}
\end{framed}\begin{framed}
\begin{align}
    \intertext{Match and temporal perspectives:\smallskip}
    & \forall i \in \{0 \nldots n{-}2\} : \forall j \in \{ i{+}1 \nldots n{-}1 \} : \nonumber \\
    & \hspace*{1em} \match[{i,j}] \in \{0..t{-}1\} \tag{V5} \label{V5} \\
    & \hspace*{1em} \match[{j,i}] \equiv \match[{i,j}] \nonumber \\
    & \hspace*{1em} \forall k \in \{0 \nldots t{-}1 \} : \nonumber \\
    & \hspace*{2em} \match[{i,j}] = k \Leftrightarrow \sigma[{i}].\timeSlot[{k}] = j \wedge \sigma[{j}].\timeSlot[{k}] = i \tag{C6} \label{C6} \\[0.1cm]
    & \forall i \in \{0 \nldots n{-}2\} : \forall j \in \{ i{+}1 \nldots n{-}1 \} \nonumber : \\
    & \hspace*{1em} \modMatch[{i,j}] \in \{0..f{-}1\} \label{V6} \tag{V6} \\
    & \hspace*{1em} \modMatch[{j,i}] \equiv \modMatch[{i,j}] \nonumber  \\
    & \hspace*{1em} \modMatch[{i,j}] = \match[{i,j}] / m \tag{C7} \label{C7} \\
    & \forall i \in \{0 \nldots n{-}1 \} : \allDifferent(\modMatch[{i}]) \tag{C8} \label{C8} \\[0.1cm]
    & \forall \tau \in \{0 \nldots t{-}1 \} : \nonumber \\
    & \hspace*{1em} \timeVar[{\tau}] \in \{(0,1) \nldots (n{-}2,n{-}1)\} \tag{V7} \label{V7} \\
    & \hspace*{1em} \forall i \in \{0 \nldots n{-}2\} : \forall  j \in \{ i{+}1 \nldots n{-}1 \} : \timeVar[{\tau}] = (i,j) \Leftrightarrow \match[{i,j}] = \tau \tag{C9} \label{C9} \\[0.1cm]
    & \totalBoatChanges = \textstyle\sum \sigma.\totalChanges \label{V8} \tag{V8} \\
    & \minimise(\totalBoatChanges) \label{C10} \tag{C10}
\end{align}
\end{framed}
\caption{Our constraint model, from a skipper perspective (top) and a match and
temporal perspective (below). The number of skippers is $n$, and $m$ is the
number of matches in a flight. The number of flights is $f = \lceil n(n-1)/m
\rceil$, and there are $t = n(n-1)/2$ matches in total.}\label{model:stage1}
\end{figure}
